Discrepancy, Coresets, and Sketches in Machine Learning

### 2019-01-31 komlos.tex
typo

Notice that these bounds are (asymptotically) tight in the context of unweighted coresets. Taking for example the bound of Fact~\ref{fct:eps1}, we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.

>>>>

Notice that these bounds are (asymptotically) tight in the context of unweighted coresets. Taking for example the bound of Fact~\ref{fct:eps1}, if we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
